\vspace{2cm} \LARGE \bf Seasonal influenza circulation patterns and projections for 2016-2017

### 2016-09-21 auspice/reports/tex/sep-2016.tex
Update references and add disclaimer to tex report.

% basic packages
\usepackage{color}
\usepackage{parskip}
\usepackage{float}
\usepackage{microtype}
\usepackage{url}

@@

>>>>

% basic packages
\usepackage{color}
\usepackage{parskip}
\usepackage{float}
\usepackage{microtype}
\usepackage{url}
\usepackage{hyperref}

@@

\textit{This is not meant as a comprehensive report, but is instead intended as particular observations that may be of relevance. Please also note that observed patterns reflect the GISAID database and may not be entirely representative of underlying dynamics. All analyses are based on the nextflu pipeline \cite{neher2015nextflu} with continual updates posted to \href{http://nextflu.org}{nextflu.org}.}
